---
title: "615_Assignment2"
author: "Lauren Marie"
date: "9/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load('dplyr', 'ggplot2', 'tidyr', 'knitr', 'stringr', 'tibble', 'readr')
```

# Allocable Aid for Official Development Assistance
```{r, echo=FALSE, include=FALSE}
source('C:/Users/ltemp/Desktop/MSSP/MA 615/615_Assignment2/wranglingcode.R', echo=FALSE)
```

The data sets used in this assignment are from [Gapminder](https://www.gapminder.org/data)

**aid_given_2007_us.csv**
Contains the data for the total amount of allocable aid for official development assistance (ODA) given by the donor countries, expressed in USD.

**health_aid_given_percent_of_aid.csv**
Contains the data pertaining to the percentage of total allocable aid for official development assistance (ODA) given by the donor countries that has been used in health.

I chose to focus on the years 1997-2006 in two of the countries that give the most amount of aid, the United States and Japan.


```{r, echo=FALSE}
source('C:/Users/ltemp/Desktop/MSSP/MA 615/615_Assignment2/visualization.R', echo=FALSE)
#figure out how to source these files then you can delete all the copied code below. keep explaination
```

Observations