---
title: "615_Assignment2"
author: "Lauren Marie"
date: "9/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load('dplyr', 'ggplot2', 'tidyr', 'knitr', 'stringr', 'tibble')
```

# Allocable Aid for Official Development Assistance

```{r}

aid<- aid_given_2007_us
names(aid)<- str_replace(names(aid), "X", "")
aidgiven<- rename(.data=aid, Country=ï..country)
aidgiven<- aidgiven %>% pivot_longer(!Country, names_to ="Year", values_to ="count")

health<- health_aid_given_percent_of_aid
names(health)<- str_replace(names(health), "X", "")
healthaid<- rename(.data=health, Country=ï..country)
healthaid<- healthaid %>% pivot_longer(!Country, names_to="Year", values_to="count")

compareaid<- left_join(aidgiven, healthaid, by=c("Year", "Country"))

compareaid<- rename(.data=compareaid, Aid=count.x, Health_Percent=count.y)
compareaid%>%kable()
is_tibble(compareaid)

plot<- function(a,b){
  {
    Country<-a
    data2<- filter(b, Country==a, Year>1996)
    c<-ggplot(data=data2)+geom_col(aes(x=Year, y=Aid, fill=Health_Percent))+ggtitle(Country)
    print(c)
  }
}
```

The data sets used in this assignment are from [Gapminder](https://www.gapminder.org/data)

**aid_given_2007_us.csv**
Contains the data for the total amount of allocable aid for official development assistance (ODA) given by the donor countries, expressed in USD.

**health_aid_given_percent_of_aid.csv**
Contains the data pertaining to the percentage of total allocable aid for official development assistance (ODA) given by the donor countries that has been used in health.

I chose to focus on the years 1997-2006 in two of the countries that give the most amount of aid, the United States and Japan.

## Allocable aid for ODA 1997-2006
### United States

```{r}
plot("United States", compareaid)
```

### Japan

```{r}
plot("Japan", compareaid)
```

#### Observations